Random Matrix Theory Tools for the Analysis of Functional Magnetic Resonance Imaging Examinations

### 2022-11-01 paper/paper/SPIE/article.tex
[WIP]

In this sense, RMT has considerable \textit{explanatory} and \textit{statistical} value: the more we
see that a system resembles an RMT system, the less we can distinguish it from one of random,
non-interacting components, and the less the system resembles an RMT system, the more
fundamentally complex and interactive the interactions.

@@

Despite the mathematical elegance and simplicity, RMT has yielded insights in variosu complex domains.

>>>>

In this sense, RMT might have real \textit{explanatory} and \textit{statistical} value: the more we
see that a system resembles an RMT system, the less we can distinguish it from one of random,
non-interacting components, and the less the system resembles an RMT system, the more
fundamentally complex and interactive the interactions.

@@

[Transition to fMRI now...]
